---
title: "Data Quality Report"
author: "Ministry of Health"
output:
  pdf_document:
    extra_dependencies: ["longtable","float"]
    latex_engine: xelatex
date: "`r Sys.Date()`"
params:
  district: NA
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE)
```

## Data Quality Report for `r params$district`

This is an automated report highlighting Facilities with possible data elements that could be outliers. 
Theses might  need to be verified. 

```{r}
library(tidyverse)
library(knitr)
library(readr)
library(kableExtra)
library(here)
library(gsheet)

#data <- read_csv("impute.csv")

data_im <- gsheet2tbl('https://drive.google.com/open?id= 1lo0YoQPgqm4p8P3WU4D9Sh9NKUw19G_L34Vf1d0TlMc')

data <- data_im %>%
  filter(district ==  params$district) %>%
  mutate(period = as.character(period))

#params$district

#"Wakiso District"

data$variable_clean <- round(data$variable_clean)
data$period <-  lubridate::ymd(data$period)

table <- data %>%
      group_by(facility,flag)  %>%
      count() %>%
      pivot_wider(names_from = flag,values_from = n) %>%
      rowwise() %>%
      mutate(total = sum(None,Outlier),
             Percentage_outliers = round(Outlier/total*100))%>%
      select(-None) %>%
      filter(Outlier > 0) %>%
    dplyr::arrange(desc(Outlier)) %>%
      rename(
        `Possible Outliers (Counts)` = Outlier,
        `Total Records Reviewed` = total, 
        `% Outliers` = Percentage_outliers) 

facilites <- unique(table$facility)

```

## Facilties with the highest counts of Possible Outliers in `r params$district` in 2023
```{r}

plot_data <- data %>%
      group_by(facility,flag)  %>%
      count() %>%
      pivot_wider(names_from = flag,values_from = n) %>%
      rowwise() %>%
      mutate(total = sum(None,Outlier),
             Percentage_outliers = round(Outlier/total*100))%>%
      select(-None) %>%
      filter(Outlier > 0) %>%
      dplyr::arrange(desc(Outlier))

plot_data %>%
  ungroup() %>%
  slice_max(Outlier,n=10)%>%
      ggplot(aes(x  = reorder(facility,Outlier),y = Outlier))+
      geom_col(fill = "#264653")+
    geom_text(aes(label = round(Outlier)), hjust = 3, color = "white", size = 4)+
  coord_flip()+
  labs(x = "", y = "Counts")+
  theme_bw()
  
```


### Summary of Facilities with Possible Outliers
There was a total of `r length(facilites)` Facilities in `r params$district` had atleast One  possible outlier in 2023 as summarised  below; 


```{r}
# ft <- flextable(table)
# ft <- autofit(ft)
# theme_vanilla(ft)

table_format = if(is_html_output()) {
  "html"
} else if(is_latex_output()) {
  "latex"
}

table %>%
  kable(format = table_format,booktabs = TRUE) %>%
    kable_styling(latex_options = c("striped","scale_down", "HOLD_position","repeat_header"))


```


## Breakdown of the Possible Outliers per Facility in 2023
```{r}

sum <- data %>%
      ungroup() %>%
      filter(flag == "Outlier") %>%
      select(-c(flag,region,district)) %>%
      relocate(indicator , .before = period) %>%
      filter(period > "2023-01-01")%>%
      dplyr::arrange(desc(period)) %>%
      rename(
        `Expected Value` = variable_clean,
        `Possible Outlier` = variable,
        `Data Element` = indicator,
        Month = period,
        Facility = facility
        )

# kt <- flextable(sum)
# kt <- autofit(kt)
# theme_vanilla(kt)

table_format = if(is_html_output()) {
  "html"
} else if(is_latex_output()) {
  "latex"
}

sum %>%
  kable(format = table_format,booktabs = TRUE) %>%
    kable_styling(latex_options = c("striped","scale_down", "HOLD_position"))
  
# knitr::kable(sum) %>%
#   kableExtra::kable_styling(latex_options  c("scale_down", "HOLD_position"))
```


